Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-07-31 threshold/draft.Rnw
Added the distribution of cov(a_i, a_j) with normal assumptions.

>>>>

\section{The distribution of $||a_i - a_j||^2$}

\begin{lemma}
\label{asymdistm1lemma}
Let $m=1$, $X_i$ and $X_j$ be distributed as $\mathcal{N}(0, \Delta_{ij})$,
with $\Delta_{ii} = 1$.  Then
\begin{equation}
\label{eqasymdist1}
|| X_i - X_j ||^2 \sim R + \frac{\Delta_{ij} + 1}{2} S + 
  \frac{\Delta_{ij} - 1}{2} T
\end{equation}
where $R$ is distributed as $\chi_2^2$ and $S$ and $T$ are $\chi_1^2$.
\end{lemma}
\begin{proof}
\begin{equation*}
||X_i - X_j||^2 = X_i^2 - 2 X_i X_j + X_j^2
\end{equation*}
$X_i^2$ and $X_j^2$ are clearly $\chi_1^2$. To derive the distribution
of the cross-product term realize
\begin{equation*}
X_i X_j = \frac{1}{4} \left(X_i + X_j\right)^2 - 
  \frac{1}{4} \left(X_i - X_j\right)^2.
\end{equation*}
$X_i + X_j$ and $X_i - X_j$ are both distributed as normal and they are 
independent
since $\mathbf{E}X_1^2 = \mathbf{E}X_2^2$. Therefore, their squares
are $\chi_1^2$ and the leading coefficients in Equation \ref{eqasymdist1}
are the respective variances.
\end{proof}

\begin{lemma}
\label{asymdistlemma}
Let $a_i$ and $a_j$ be any two columns of the matrix 
$B \in \mathcal{R}^{m \times n}$, sampled from 
$\mathcal{N}(0, \Delta/m)$ where $\Delta_{ii} = 1$ for $1 \leq i \leq n$.
Then
\begin{equation*}
||a_i - a_j||^2 \xrightarrow[m]{D} \mathcal{N} \left(2 + \Delta_{ij},  
  \frac{5 + \Delta_{ij}^2}{m} \right) 
\end{equation*}
\end{lemma}
This result follows by applying the central limit theorem to
the result in Lemma \ref{asymdistm1lemma} where $m$ is appropriately large.
